Fréchet Distance

### 2022-11-21 docs/paper.tex
Hausdorff distance graphics

% Hausdorff distance
The commonly known \textit{Hausdorff distance} can be understood 
as the largest distance between any two points on the curves 
and is calculated by \autoref{eq_hausdorff_distance} \cite{alt_computing_1995}.

@@

\begin{figure}[ht]
  % TODO: insert figure
  \caption[Hausdorff distance of two dissimilar curves]{The two shown curves are dissimilar (in a common sense) depsite having a small Hausdorff distance.}
  \label{fig_hausdorff_distance_bad_example}
\end{figure}

>>>>

% Hausdorff distance
The commonly known \textit{Hausdorff distance} can be understood 
as the largest distance between any two points on the curves. 
For each curve, a point with the maximum shortest distance to a point on the other curve is searched for, see \autoref{fig_hausdorff_distance_example}.
The Hausdorff distance is mathematically formulated as stated in \autoref{eq_hausdorff_distance} \cite{alt_computing_1995}.

@@

\begin{figure}[ht]
  % TODO: insert figure
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-example.pdf}
      }
      \caption{Hausdorff distance between the red curve $P$ and green curve $Q$. }
      \label{fig_hausdorff_distance_example}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.45\textwidth}
      \resizebox{\textwidth}{!}{
        \includegraphics[width=\textwidth]{images/hausdorff/hausdorff-distance-bad-example.pdf}
      }
      \caption[Hausdorff distance of two dissimilar curves]{Two dissimilar curves with a small Hausdorff distance.}
      \label{fig_hausdorff_distance_bad_example}
  \end{subfigure}
  \caption[Hausdorff distance examples]{Hausdorff distance examples.}
  \label{fig_hausdorff_distance_examples}
\end{figure}
